Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-06 analysis/paper/paper.Rmd
Add scientific names to introduction text

Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007]. In AWD rice fields are exposed to several dry phases during the growth period without exposing the plants to water stress. In order to avoid yield decline under AWD “safe” thresholds have been developed. Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [@Richards2014]. Fields are furthermore kept flooded during the flowering period. Besides saving water AWD also reduces greenhouse gas (GHG) emissions of rice fields, which is a substantial factor in the GHG budget of rice producing countries, by around 50% [@Yan2005; @Sander2015].

@@

We therefore established field experiments in order to…

>>>>

Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice (\emph{Oryza sativa L.}) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007]. In AWD rice, fields are exposed to several dry phases during the growth period without exposing the plants to water stress. In order to avoid yield decline under AWD “safe” thresholds have been developed. Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [@Richards2014]. Fields are furthermore kept flooded during the flowering period. As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50% [@Yan2005; @Sander2015].

@@

We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (\emph{Rhizoctonia solani} Kühn) [(teleomorph: \emph{Thanatephorus cucumeris} (A.B. Frank) Donk.] of rice.
